Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-13 emsoft-2019/Motiv.tex
Fig 2 with subfigure

		\draw [draw,->, align=center] (RMPC) -- node [left] {High-precision controller}(Uij);
		\draw [->] (Uij) -- node [left] {$e$}(decide);
		\draw [->] (decide) -- node [left,pos=.3] {Yes} (done);
		\draw [->] (decide) -- node[pos=0.99] {} 
		node [] {No} (delta);
		\draw [->] (delta) |- node [above] {} (RMPC);
		\draw [->] (done) -- node [above] {} (output);
		%\node [block2, scale=0.7] at (1.3,-.42) {MATLAB} ;
		%\node [block2, scale=0.7] at (1.65,-2.95) {Daisy} ;
		%\node [block2, scale=0.7] at (1.58,-7) {Daisy} ;
		\end{tikzpicture}\par}
	%	\hspace{\fill} 
	%\end{center}
	%\end{adjustbox}
	\caption{Overview of the proposed memory-efficient robust MPC control design.}
	\label{fig:overview}
\end{figure}

@@

\begin{figure}[t]
	\begin{tabular}{cc}
	\includegraphics[width=2cm,height=3cm]{Figs/inverted_pendulum.pdf}&	\includegraphics[width=6cm,height=4cm]{Figs/regs.jpg}\\
	(a)&(b)
	\end{tabular}
	\caption{(a) Inverted pendulum; (b) 2-D plot of polyhedral partitions for an explicit MPC applied to the inverted pendulum.}
	\label{fig:inverted_pendulum}
\end{figure}

@@

>>>>

		\draw [draw,->, align=center] (RMPC) -- node [left] {High-precision controller}(Uij);
		\draw [->] (Uij) -- node [left] {$e$}(decide);
		\draw [->] (decide) -- node [left,pos=.3] {Yes} (done);
		\draw [->] (decide) -- node[pos=0.99] {} 
		node [] {No} (delta);
		\draw [->] (delta) |- node [above] {} (RMPC);
		\draw [->] (done) -- node [above] {} (output);
		%\node [block2, scale=0.7] at (1.3,-.42) {MATLAB} ;
		%\node [block2, scale=0.7] at (1.65,-2.95) {Daisy} ;
		%\node [block2, scale=0.7] at (1.58,-7) {Daisy} ;
		\end{tikzpicture}\par}
	%	\hspace{\fill} 
	%\end{center}
	%\end{adjustbox}
	\caption{Overview of the proposed memory-efficient robust EMPC control design.}
	\label{fig:overview}
\end{figure}

@@

@@

\begin{figure}[t]
	\centering
  \begin{subfigure}[b]{0.33\columnwidth}
      \includegraphics[width=\textwidth]{Figs/inverted_pendulum.pdf}
      \vspace{0.05cm}
      \caption{}
  \end{subfigure}
  %~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
  \begin{subfigure}[b]{0.66\columnwidth}
      \includegraphics[width=\textwidth]{Figs/regs.jpg}
      \caption{}
  \end{subfigure}
	\caption{(a) Inverted pendulum; (b) 2D plot of polyhedral partitions for an EMPC applied to the inverted pendulum.}
	\label{fig:inverted_pendulum}
\end{figure}
